Calibrating the pixel-level Kepler imaging data with a causal data-driven model \\

### 2015-03-28 documents/cpm.tex
changes to Hogg's comments

Once we have obtained the parameters $a_{m,n,m'}$ and $b_{m,n,v}$ corresponding to a particular data point $I_{m,n}$,
  we can make a \emph{prediction} $I^{\ast}_{m,n}$ for the intensity at that pixel.
By construction of our objective function, this is truly a prediction,
  in the sense that the optimization (or solve) that produced the parameters
  (and thus the prediction)
  did not make use of $I_{m,n}$ itself,
  nor even any of the pixel values that are nearby in angle or time
  (as described above).
  With all the predicted pixel values $I^{\ast}_{m,n}$ of the target star,  
  our new stellar flux estimates,
  what we will call the ``\name\ prediction'',
  is constructed from the \name\ pixels
  in precisely the same way as the official \Kepler\ SAP photometry
  is constructed from the Target Pixel Files.
That is, we perform a weighted sum of \name\ predicted pixels $I^{\ast}_{m,n}$ with weights $w_m$,
  all of which are either zero or unity,
  and we adopt precisely the same weight assignments as are adopted in the SAP photometry;
  in equations, the flux estimate $S_n$ at time $t_n$ of the target star is given by
\begin{eqnarray}
S_n = \sum_m w_m\,I^{\ast}_{m,n}
\quad ,
\end{eqnarray}
where the sum is over the $M$ pixels that are associated with the target star and the weight $w_m$ is unity for pixels in the optimal
aperture while zero outside the optimal aperture.
 \Bernhard{if the sum is only over the pixels of the target star, then all $w_m$ are equal to 1 and they can be dropped}.
 \Dun{$w_m$ is 0 out of the optimal aperture,  we've added some words to explain it.}
As we have noted above and below, these photometric estimators are not optimal for any purpose,
  but improving them is beyond the scope of this project.

It is worth to mention that the \name\ prediction $S_{n}$ is constructed from predicted pixel value 
  without any information about transits in the target star due to the train-and-test framework.
  \Bernhard{changed this --- I didn't understand it} \Dun{Does it look better now?} 
Therefore, it can be regarded as a light curve without transit signal. 
Based on this idea, 
  we can construct the ``\name\ flux''% 
  (where the inverted commas indicate that it is not a flux in the sense that stellar variability is not preserved)% 
  to be the relative residual between \name\ prediction and SAP Flux $F_{n}$
\begin{eqnarray}
\delta_{n}&\equiv&\frac{F_{n} - S_{n}}{S_{n}}
\quad .
\end{eqnarray}
The \name\ flux is 
In some sense, it is this relative residual that contains the exoplanet transit signals we seek. 
That is, a transit creates a negative residual away from the prediction, 
  and the amount of relative residual is just the fraction of the light eclipsed by the planet (the transit depth).

\subsection{Hyper-parameters}
In the description of \name, 
  we introduce 4 hyper-parameters---number of predictor stars Q (or number of predictor pixels P), 
  number of autoregressive components S, and the two regularization strength $\lambda_{a}$ and $\lambda_{b}$.
To set these 4 hyper-parameters, 
  in principle we need to run cross-validation on every single star to optimize the performance of \name.
But optimizing in this 4-dimensional space is expensive, 
  especially in \name\ we need to solve thousands of linear systems with thousands of parameters. 
Therefore, in this paper, 
  we just set a general set of ``default'' hyper-parameters ($P=4000$, $Q=3$, $\lambda_a=1e5$, $\lambda_a=1e5$), 
  which works well in most of the stars without highly variability. 
To show how this general set of hyper-parameters performs, 
  here we present a typical comparison between optimized and default hyper-parameters 
  in Fig~\ref{hyperparameter}.\Bernhard{maybe explain somewhere how SNR is calculated}  
We can see that, in Fig~\ref{hyperparameter}, 
  there is less variation in the \name\ flux from optimized hyper-parameters (green points in second panel) 
  than from the default one (red points in the bottom panel). 
In addition, the optimized flux has higher signal to noise ratio of the known transit than the default. 
However, the performance of default hyper-parameters is acceptable 
  and we will use this set of hyper-parameters throughout rest of the paper 
  to show the general performance of \name.

@@

\caption{
  \label{fluxes} 
  Corrected fluxes using \name, for 12 example stars, 
    spanning the main magnitude (brightness) range encountered. 
  In first column plots, we consider bright stars with magnitude from 9 to 10.5, 
    second cloumn are stars with magnitude from 11 to 12.5,  
    and the third column are faint stars with magnitude above 13. 
  In the first two rows, we present some quiet stars. 
  In all three panels, the top panel shows the SAP flux (black) and the \name\ regression (red), 
    i.e., our prediction of the star from other stars. 
  The middle panel shows the \name\ flux corrected using the regression, and the bottom shows the PDC flux. 
  One can see that the \name\ flux curve preserves the exoplanet transits (little downward spikes), 
    while removing a substantial part of the variability present in the PDC flux. 
  Both the bottom two rows present some variable stars with slow and fast variability. 
  For the variable stars, we did not present the PDC comparison, 
    since the PDC flux try to preserve intrinsic steller variability.}
\end{figure}

@@

\section{Discussion}
We have presented a simple yet highly effective method that works in pixel-level 
based on the causal structure of the \Kepler\ data to calibrate the \Kepler\ light curves, 
which is intended to search exoplanets. 
However, based on our assumption of the causal structure of the \Kepler\ 
data, if we turn off the auto-regressive components and keep the predictors from other
stars working  in the \name, we should be able to still remove the systematics while
preserve the intrinsic stellar  variability, since there is no reason that these independent
stars can be used to predict the stellar variability of the target star. However, in fact, we
can not preserve the stellar variability just by turning off the auto-regressive 
components. One possible reason can be that, since our model is so flexible 
(thousands of parameters), in principle it can fit any functions. In this sense, we should 
run cross-validation with the auto-regressive components turned off and to find out how
many pixels from other stars we need to just remove systematics while preserve stellar
variability, but in fact we do not have a good criterion to check how well we preserve
stellar variability in cross-validation because we do not have enough knowledge of the 
true stellar variability. Thus for the time being, we just focus on producing well-
calibrated light curves for searching exoplanets, but in long term, we are looking
forward to find a method to preserve the stellar variability.

>>>>

Once we have obtained the parameters $a_{m,n,m'}$ and $b_{m,n,v}$ corresponding to a particular data point $I_{m,n}$,
  we can make a \emph{prediction} $I^{\ast}_{m,n}$ for the intensity at that pixel.
By construction of our objective function, this is truly a prediction,
  in the sense that the optimization (or solve) that produced the parameters
  (and thus the prediction)
  did not make use of $I_{m,n}$ itself,
  nor even any of the pixel values that are nearby in angle or time
  (as described above).
  With all the predicted pixel values $I^{\ast}_{m,n}$ of the target star,  
  our new stellar flux estimates,
  what we will call the ``\name\ prediction'',
  is constructed from the \name\ pixels
  in precisely the same way as the official \Kepler\ SAP photometry
  is constructed from the Target Pixel Files.
That is, we perform a weighted sum of \name\ predicted pixels $I^{\ast}_{m,n}$ with weights $w_m$,
  all of which are either zero or unity,
  and we adopt precisely the same weight assignments as are adopted in the SAP photometry;
  in equations, the flux estimate $S_n$ at time $t_n$ of the target star is given by
\begin{eqnarray}
S_n = \sum_m w_m\,I^{\ast}_{m,n}
\quad ,
\end{eqnarray}
where the sum is over the $M$ pixels that are associated with the target star and the weight $w_m$ is unity for pixels in the optimal
aperture while zero outside the optimal aperture.
As we have noted above and below, these photometric estimators are not optimal for any purpose,
  but improving them is beyond the scope of this project.

Because of the train-and-test framework,  
  we expect the \name\ prediction $S_{n}$ to be a prediction of%
  what the star lightcurve would have under the influence of the spacecraft but with no exoplanet signal 
Based on this idea, 
  we can construct the ``\name\ flux''% 
  (where the inverted commas indicate that it is not a flux in the sense that stellar variability is not preserved)% 
  to be the relative residual between \name\ prediction and SAP Flux $F_{n}$
\begin{eqnarray}
\delta_{n}&\equiv&\frac{F_{n} - S_{n}}{S_{n}}
\quad .
\end{eqnarray} 
In some sense, it is this relative residual--- the \name\ flux that contains the exoplanet transit signals we seek. 
That is, a transit creates a negative residual away from the prediction, 
  and the amount of relative residual is just the fraction of the light eclipsed by the planet (the transit depth).

\subsection{Hyper-parameters}
The \name\ has 4 hyper-parameters--- 
  the number of predictor stars Q (or number of predictor pixels P), 
  the number of autoregressive components S, 
  and the two regularization strength $\lambda_{a}$ and $\lambda_{b}$.
To set these 4 hyper-parameters, 
  in principle we need to run something like a cross-validation on every single star to optimize performance.
But optimizing in this 4-dimensional space is expensive, 
  especially since in the \name\ we need to solve thousands of linear systems, 
  each of which has thousands of free parameters. 
Therefore, in this paper, 
  we just set a general set of ``default'' hyper-parameters ($P=4000$, $Q=3$, $\lambda_a=1e5$, $\lambda_a=1e5$), 
  which works well in most of the stars without high variability. 
To show how this general set of hyper-parameters performs, 
  we present a few comparison between optimized and default hyper-parameters 
  in Fig~\ref{hyperparameter}.\Bernhard{maybe explain somewhere how SNR is calculated}  
We can see that, in Fig~\ref{hyperparameter}, 
  there is less variation in the \name\ flux% 
  when we use optimized hyper-parameters (green points in second panel)% 
  than when we use the default one (red points in the bottom panel). 
In addition, the optimized flux has higher signal to noise ratio of the known transit than the default. 
However, the performance of default hyper-parameters is acceptable 
  and we will use this set of hyper-parameters throughout the rest of the paper 
  to show the general performance of \name.

@@

\caption{
  \label{fluxes} 
  Corrected fluxes using \name, for 12 example stars, 
    spanning the main magnitude (brightness) range encountered. 
  In first column plots, we consider bright stars with magnitude from 9 to 10.5, 
    second cloumn are stars with magnitude from 11 to 12.5,  
    and the third column are faint stars with magnitude above 13. 
  In the first two rows, we present some quiet stars. 
  In all three panels, the top panel shows the SAP flux (black) and the \name\ regression (red), 
    i.e., our prediction of the star from other stars. 
  The middle panel shows the \name\ flux corrected using the regression, and the bottom shows the PDC flux. 
  One can see that the \name\ flux curve preserves the exoplanet transits (little downward spikes), 
    while removing a substantial part of the variability present in the PDC flux. 
  Both the bottom two rows present some variable stars with slow and fast variability. 
  For the variable stars, we did not present the PDC comparison, 
    since the PDC flux try to preserve intrinsic stellar variability.}
\end{figure}

@@

\section{Discussion}
We have presented a simple yet highly effective method that works in pixel-level 
based on the causal structure of the \Kepler\ data to calibrate the \Kepler\ lightcurves, 
which is intended to search exoplanets. 
However, based on our assumption of the causal structure of the \Kepler\ 
data, if we turn off the auto-regressive components and keep the predictors from other
stars working  in the \name, we should be able to still remove the systematics while
preserve the intrinsic stellar  variability, since there is no reason that these independent
stars can be used to predict the stellar variability of the target star. However, in fact, we
can not preserve the stellar variability just by turning off the auto-regressive 
components. One possible reason can be that, since our model is so flexible 
(thousands of parameters), in principle it can fit any functions. In this sense, we should 
run cross-validation with the auto-regressive components turned off and to find out how
many pixels from other stars we need to just remove systematics while preserve stellar
variability, but in fact we do not have a good criterion to check how well we preserve
stellar variability in cross-validation because we do not have enough knowledge of the 
true stellar variability. Thus for the time being, we just focus on producing well-
calibrated light curves for searching exoplanets, but in long term, we are looking
forward to find a method to preserve the stellar variability.
